---
title: "My answers"
author: "My name"
date: "2023-03-27"
output: html_document
---


```{r}
# Write your answer here
```


Some of the exercises in this lab are based on those found in  [Wickham and Grolemund, R for Data Science](https://r4ds.had.co.nz/).



# Getting started
(@) Install the `tidyverse` package (only required if this is the first time you are using tidyverse on this computer). 

Uncomment this following line (i.e. remove the `#`) and change the chunk option to `eval=FALSE`. Knit your file and see what happens.

```{r install_tidy, eval=FALSE}
#eval = FALSE , code will not be run
install.packages("tidyverse")
```

(@) Load the `tidyverse` package
```{r load_tidy, message = FALSE}
# if show the message
library(tidyverse)
```


```{block, box.title = "Tip", box.body = list(fill = "lightblue")}
#You can get help in R by typing "?" followed by the function name. For example ?ggplot

?ggplot
```

# R Markdown 


(@) You can change what gets displayed when you compile your Rmd file by changing the chunk options.

Some examples are shown below. Look at the code in the Rmd file and output in the PDF file and figure out what each one does.

* `echo = FALSE`

* `echo = TRUE`
```{r chunk-demo2, echo = TRUE}
x <- 1:10
x
```

* `results = "hide"`
```{r chunk-demo3, results = "hide"}
x <- 1:10
x
```

* `results = "hold"`
```{r chunk-demo4, results = "hold"}
x <- 1:10
x
y <- 2:11
y
```


* `include = TRUE` (change to FALSE)
```{r chunk-demo5, include = TRUE}
z <- 1:10
```


(@) Have a look at this page <https://yihui.org/knitr/options/#code-chunk> to get more information about different chunk options.


(@) You can add code within an R Markdown paragraph. For example, the mean of `z` is `r mean(z)` (inspect within Rmd file).
 
# dplyr

(@) Load and inspect the `flights` dataset

```{r}
library(nycflights13)
flights
```

(@) What does the variable "air_time" represent?

```{r}
# Write your answer here
?flights
#Amount of time spent in the air, in minutes
```


(@) Create a dataset called `march1` containing flights which departed on 1st March 2013.
How many flights departed on 1st March 2013?

```{r}
# Write your answer here
march1 = filter(flights,year==2013 & month==3 & day==1)
nrow(march1)
```


(@) For the flights which departed on 1st March 2013, create a new variable called `max_delay` which contains the maximum of the departure delay and the arrival delay.  Arrange in descending order by the new variable so the first row contains the flight with the largest 
departure or arrival delay. Which flight had the greatest delay and how long was the delay?

Hint: You will need to use the command `rowwise()` (see PDF file)



```{r}
# Write your answer here
flight_max_delay <- flights %>% 
  filter(year==2013 & month==3 & day==1) %>%
  rowwise() %>%
  mutate(max_delay = max(dep_delay,arr_delay,na.rm = TRUE)) %>%
  arrange(-max_delay) %>%
  select(max_delay,everything())
  
head(flight_max_delay, 1)
```


(@) For the flights which departed on 1st March 2013, what was the destination of the one with the biggest departure delay?

```{r}
# Write your answer here

flight_max_delay <- flights %>% 
  filter(year == 2013 & month == 3 & day == 1) %>%
  filter(dep_delay == max(dep_delay, na.rm = TRUE))

flight_max_delay$dest

#row_number(flight_max_delay) #flight_max_delay$dest
```



(@) Which destination has the greatest mean departure delay in 2013? Hint: use `group_by` and `summarise`

```{r}
# Write your answer here
flights %>%
  filter(year==2013) %>% 
  group_by(dest) %>% 
  summarise(mean_col = mean(dep_delay,na.rm=TRUE)) %>%
  arrange(-mean_col) %>%
  select(dest,mean_col)  # or head(1)


```


(@) Use summarise to determine the number of flights by each carrier.

Hint: `summarise(n=n())`
```{r}
# Write your answer here

flights %>%
  group_by(carrier)%>%
  summarise(n_flights=n()) %>%
  arrange(-n_flights)

```


(@) For flights which departed on 1st March, create a boxplot showing the departure delay, with one box for each "carrier". Which airline seems to have the worst on-time performance?

```{r}
# Write your answer here
df1 = flights %>%
  filter(day==1 & month==3 ) %>%
  select(dep_delay,carrier)

ggplot(data = df1)+
  geom_boxplot(mapping = aes(x=carrier,y=dep_delay))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  coord_flip()
```



# tibble


(@) Consider the iris data set.

  - Run the following code and inspect the difference in output.
```{r inspect_iris, results="hide"}
iris
(iris_tb <- as_tibble(iris))
```

 

  - Using `iris_tb`, create a ggplot to compare `Sepal.Width` and `Sepal.Length`, with a different colour for each `Species`. Write 2 - 3 sentences describing your plot.

```{r}
# Write your answer here
ggplot(data = iris_tb) +
  geom_point(mapping = aes(x=Sepal.Width,y= Sepal.Length,color=Species))+
  labs(title="comparison of Comparison of Sepal Width and Sepal Length by Species", x="Sepal.Width",y="Sepal.Length",color="diff Species")

```



```{r}
# Write your answer here
```


(@) Create the following tibble.

```{r create_annoying}
set.seed(123414)
annoying <- tibble(
  `1` = 1:10,
  `2` = `1` * 2 + rnorm(length(`1`))
)
```

Practice referring to non-syntactic names in the following data frame by:

  - Extracting the variable called 1. The desired output is shown below.

```{r}
# Write your answer here
annoying$`1`
annoying$`2`

```

  
  - Plotting a scatterplot of 1 vs 2.
```{r}
# Write your answer here
ggplot(annoying, aes(x=`1`,y=`2`)) +
  geom_point()+
  labs(title = "1 VS 2", x="var 1" ,y="var 2")


```


  - Creating a new column called 3 which is 2 divided by 1. The desired output is shown below.

```{r}
# Write your answer here
annoying = annoying %>%
  mutate(`3`=`2`/`1`)

annoying
```


  - Renaming the columns to one, two and three. The desired output is shown below.
  
```{r}
# Write your answer here
annoying2 <- annoying %>%
  mutate(one=`1`,two=`2`,three=`3`)%>%
  select(one,two, three)

annoying3 <- annoying %>%
  rename(one=`1`,two=`2`,three=`3`)

annoying3
```



# Application

Pick one of the following datasets:

* `ggplot2::mpg`
* `nycflights13::flights`
* `ggplot2::diamonds`

(@) Look at the help page in R for your chosen dataset, e.g. `?flights`.
```{r}
# Write your answer here
#?mpg
mpg
```

(@) Write 3 questions about this dataset.

e.g. How many flights were late on Christmas day?

(@) Transform the data and/or create an summary statistics to investigate each of your questions.

```{r}
# 1. how many cars has more than 4 cyl in cty 18
mpg %>%
  filter(cyl>4 & cty==18) %>%
  summarise(n_n = n())

# 2. how many kinds of car and count.
mpg %>%
  group_by(manufacturer,model) %>%
  summarise(model_count=n()) %>%
  arrange(-model_count)

#3 which cty's car has max mean of year?
mpg %>%
  mutate(age=2024-year) %>%
  group_by(cty) %>%
  summarise(mean_year = mean(age)) %>%
  arrange(-mean_year) %>%
  head(10)%>%
  select(mean_year,cty)
  


```


# Further practice

(@)  Read R4DS chapters 5, 6, 10 and do the exercises.  
