---
title: "My answers"
author: "My name"
date: "2023-04-06"
output: html_document
---


```{r}
# Write your answer here
```


Some of the exercises in this lab are based on those found in  [Wickham and Grolemund, R for Data Science](https://r4ds.had.co.nz/).



# Getting started

(@) In this lab we will need a number of packages. 

- Install them, if required, by uncommenting the following code.
```{r installPackages}
# List of packages
packages <- c("tidyverse", "readxl", "lubridate")

# Find packages that are not installed
packages_to_install <- packages[!(packages %in% installed.packages()[,"Package"])]

# Install required packages
# if(length(packages_to_install) > 0){
#   install.packages(packages_to_install,
#                    dependencies=TRUE))
# }
```
- Load the packages
```{r loadPackages, results = "hide"}
# Load new packages
sapply(packages, library, character.only=TRUE)
```


```{block, box.title = "Tip", box.body = list(fill = "lightblue")}
You can get help in R by typing "?" followed by the function name. For example ?ggplot
```


# Projects

(@) Start a new R project called "COMP824", create within a new directory on your H drive or One Drive (uni computers) or within your user directory (on your own computer)

(@) Check the working directory using `getwd()`

(@) Create two new directories within your project called "labs" and "data".


(@) Download "COMP824_lab_week06_answer.Rmd" from Canvas and save in the labs directory.

(@) Knit the file. You will write your answers to the following questions in that file.

(@) Project Directory

If your project has subfolders, e.g. one for scripts, one for data etc, 
then you need to change the working directory to the project directory when knitting.
By default, the working directory when knitting is the location of the RMD file.
If your project has a subfolders and your RMD is within one of those folders, then
this will take it back up to the project directory. 

More info: <https://bookdown.org/yihui/rmarkdown-cookbook/working-directory.html>

The following code chunk will set the directory to the one above where your Rmd file is saved.



 

# Application - Weather Data


(@)  Download the file `auckland_weather.csv` from Canvas and save in the "data" folder within your COMP824 project directory.  Open the file and note some of the issues that you might face when importing into R.

(@) Import the file `auckland_weather.csv` into R using `read_csv()`.  Check that the date column has been imported as `dttm`. 



```{r}
# Write your answer here
```



(@) Use the R function `dplyr::arrange` to sort the weather data in order of wind speed (in descending order).
Which day and time was the windiest?  
```{r}
# Write your answer here
```


(@) Use the R function `dplyr::filter` to print the records which had a wind speed of between  of over 28 and 30 knots. Your result should have 9 rows.

Hint: Use the function `between()`.

```{r}
# Write your answer here
```


(@) What is the median wind speed? What percentage of records have a wind speed equal to the median? What percentage of records have a wind speed of this value or less?

```{r}
# Write your answer here
```



(@) Use `ggplot()` to create a histogram of wind speed in Auckland Choose a `binwidth` of 5mm. 

```{r}
# Write your answer here
```


(@) Create a dataset `daily_weather` containing the daily high and low temperatures.

```{r}
# Write your answer here
```


(@) Create a line graph with two lines, showing the high and low temperatures. Adjust the labels. Save your plot as the object `p`.

```{r}
# Write your answer here
```


(@) Customise the appearance of the dates in your previous plot using `scale_x_date`.

-  What does the following code do?



-  Modify the code to show the date for the start of each week. 

```{r}
# Write your answer here
```


-  Change the appearance of the date to show yyyy-mm-dd for each week, and change the direction of the text to be vertical.
```{r}
# Write your answer here
```



# Forbes Richest Athletes


(@)  Download the dataset `Forbes_richest_athletes.csv` from Canvas and import into R.


```{r}
# Write your answer here
```


```{r}
# Write your answer here
```

(@) Data cleaning


-  Use the command `mutate` to create a new variable containing the `Sport` in lower case.

```{r}
# Write your answer here
```


-   Use the command `rename` to rename the earnings variable to `earnings`.

```{r}
# Write your answer here
```


(@) Use R to investigate the following:

-   How many athletes are included each year?

```{r}
# Write your answer here
```


-   Which soccer player earns the most?

```{r}
# Write your answer here
```


-  Which athlete has appeared the most times in this dataset?

Hint: use the function `count`

```{r}
# Write your answer here
```



-  Which sport has the richest athletes?

Hint: think about how you will define "richest athletes". There are multiple answers.
```{r}
# Write your answer here
```



(@) Write your own question of interest about the richest athletes and use the dataset to investigate it.



# Further activities

(@)  Review the examples in the lecture notes
(@)  Read R4DS chapters for this week and do the exercises.

