---
title: "My answers"
author: "My name"
date: "2023-05-03"
output: html_document
---


```{r}
# Write your answer here
```

Some of the exercises in this lab are based on those found in  [Wickham and Grolemund, R for Data Science](https://r4ds.had.co.nz/).


## Getting started

(@) In this lab we will need a number of packages. 

- Install them, if required, by uncommenting the following code.
```{r installPackages}
# List of packages
packages <- c("tidyverse", "nycflights13")

# Find packages that are not installed
packages_to_install <- packages[!(packages %in% installed.packages()[,"Package"])]

# Install required packages
# if(length(packages_to_install) > 0){ install.packages(packages_to_install,                    dependencies=TRUE)) }
```
- Load the packages
```{r loadPackages, results = "hide"}
# Load new packages
sapply(packages, library, character.only=TRUE)
```


```{block, box.title = "Tip", box.body = list(fill = "lightblue")}
You can get help in R by typing "?" followed by the function name. For example ?ggplot
```


## Joins

(@) Consider the following data sets about student grades.

  - Run the following code and inspect the outputs.
```{r inspect_tibbles, results="hide"}

COMP824exams <- tribble(
  ~studID, ~exam_mark,
     1, "A",
     2, "B",
     3, "C+"
)
COMP824classlist <- tribble(
  ~studentID, ~name, ~programme,
     1, "Charlotte", "CIS",
     2, "Zoe", "CIS",
     3, "Caitlin", "MA",
     4, "Abel", "MSc"
)

STAT800classlist <- tribble(
  ~studentID, ~name,
     1, "Charlotte",
     2, "Zoe",
     6, "Conor",
     7, "Archie"
)

```

Use the appropriate \verb|join| function to create a dataset that can answers the following questions.

- Create a dataset containing the name, ID and exam mark of all COMP824 students. Include students who didn't sit the exam.

```{r}
# Write your answer here
```



- Create a dataset containing the name, ID and exam mark of the COMP824 students who sat the exam.  

```{r}
# Write your answer here
```


- Create a dataset containing 
the name, ID and programme of the COMP824 students who sat the exam.

```{r}
# Write your answer here
```



- Which students didn't sit the COMP824 exam?


```{r}
# Write your answer here
```


- Create a dataset containing the name and ID of all students studying either COMP824 **or** STAT800 or both.
Ensure your new dataset has only 2 columns: one for ID and one for name.

```{r}
# Write your answer here
```



- Create a dataset containing the name and ID of all students studying both COMP824 **and** STAT800.
Ensure your new dataset has only 2 columns: one for ID and one for name.

```{r}
# Write your answer here
```


## Flights
(@)  Load the package `nycflights13`. Use the appropriate \verb|join| function to create a dataset that can answer the following questions.
You will need to you some other functions well (e.g. \verb|filter|).

- Create a table showing the names of the destinations that JetBlue Airways flies to.  Include a column showing the number of flights to each destination.

Start from this code:
```{r jetblue_starter}
selected_airlines <- airlines %>% filter(name %in% c("JetBlue Airways"))
```

 
```{r}
# Write your answer here
```

 
- What destinations do both JetBlue Airways and United Air Lines Inc (UA) fly to?
 
```{r}
# Write your answer here
```


(@) Use ggplot to construct a bar plot showing the number of flights per month. Add a title and subtitle to your plot.
```{r}
# Write your answer here
```

 
 (@)  Join flights and airports plot flight paths of 10 flights using longitude and latitude.
 
```{r}
# Write your answer here
```

 
 
 (@) Challenge:  Create a plot showing a line between the 20 most common origin/destination pairs. Use line thickness to represent the frequency with which flights fly between the two locations, and colour to represent the origin.
 
```{r}
# Write your answer here
```



```{r}
# Write your answer here
```



```{r}
# Write your answer here
```

 
 
 
## Further practice

(@)  Review the examples in the lecture notes
(@)  Read R4DS chapters 13 and do the exercises.

