---
title: "| COMP828 Assignment \n| Semester 1 2024\n"
author: |
  | STUDENT NAME
  | ID Number: 1234567
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    number_sections: yes
documentclass: article
classoption: a4paper
fontsize: 11pt
header-includes:
- \renewcommand{\thesection}{Q\arabic{section}}
- \renewcommand{\thesubsection}{\alph{subsection})}
- \usepackage{fullpage}
- \usepackage{fourier}
---
 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE)

# The following may be needed if your computer's language is not English
#Sys.setlocale("LC_TIME", "English_New Zealand")
```

# Load \& extract the data

```{r loadPackages, message=FALSE, results="hide", echo=FALSE, message=FALSE, warning=FALSE}
requiredPackages <- c("knitr",  "tidyverse", "readr")
packages_to_install <- requiredPackages[
                        !(requiredPackages %in% installed.packages()[,1])]

# Uncomment this line to install the packages
#if(length(packages_to_install)>0 ) install.packages(packages_to_install, 
#                                                    dependencies=TRUE)

# Load
sapply(requiredPackages, library, character.only=TRUE)
 
```

<!-- Hint: use the "Import Dataset" button in RStudio to check that syntax for importing the csv file. You'll need to change the filename below -->

Download the csv file
```{r loadData}
library(tidyverse)
sales_all <- read_csv("COMP828_sales_data.csv")
```

\newpage
# Explore the sales data

## Date range

## Number of stores

## Total price

## Discussion about total price


\newpage
# Analysis of monthly sales data

## Compute monthly sales

## Plot of monthly sales

## Discussion about monthly sales


\newpage
# Analysis of store performance

## Compute total sales per store

## Plot of total sales per store

## Additional performance metric (rename this section)

## Plot of additional performance metric (rename this section)

## Discussion of store performance




\newpage

\appendix
# Appendix: R Environment
```{r r_environ}
format(Sys.time(), '%d %B %Y')
sessionInfo()
```